Strotor: A Minimalistic Approach to \\ Exploring Large Hierarchical Data

### 2014-04-15 paper/paper.tex
...

Using 4 keys might be okay on these devices, but it would be much better
if we could do the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate two key signals based on the direction of the rotation.
%
We have developed a new navigation technique where only two keys are required
for exploring large hierarchical data, and implemented the system on
a rotating device ``Strotor''.

@@

@@

Stroter's behavior is based on the following simple principles:

\begin{enumerate}
\item Display the selected element, its siblings, its ancestors and their siblings,
and highlight the selected element.
\item If the selected element has children, wait for a little moment,
select the first child, and perform 1.
As a result, all the siblings of the newly selected element appear in the list.
\item When a user types U or D, select the element that is displayed next to the currently
selected element and perform 1.
If the depth of the newly selected element is different from the currently
selected element, siblings of the currently selected element will disappear.
\end{enumerate}

We will show how these works, using a hierarchical data structure of
shops in a shopping mall shown in Figure 1.
Rectangles with thick border represent categories, and
other rectangles represent individual shops.
We use two keys, "U" (up key) and "D" (down key), for the navigation.

\begin{figure}[H]
% \includegraphics[width=70mm]{figures/fig1.pdf}
\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
\caption{Shops in a shopping mall.}
\label{fig1}
\end{figure}

When the system starts, only the shops and categories
at the top level are displayed (Figure 2).
When the user types D,
the second element (Stationery store) is selected (Figure 3).

@@

If the user types D two more times, 
\tsf{Food/drink} category is selected (Figure 4).
If the user stops typing keys and waits for a moment, the shops under the \tsf{Food/drink}
category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure 5).

@@

When the user types D twice and stops typing,
\tsf{Fresh grocery} category is selected (Figure 6), and
the shops under the category is automatically selected (Figure 7).

@@

When the user types U here, \tsf{Fresh grocery} is selected,
the shops under \tsf{Fresh grocery} disappears (Figure 6).
If the user types U two more times, the display changes to Figure 5,
and one more typing U will generate? Figure 4.

If the user types D in Figure 4, the next visible entry
(\tsf{Clothing}) is selected (Figure 8), and then change to Figure 9.

@@

When the user types D twice in Figure 7,
\tsf{Clothing} is selected, and Figure 8 appears.

In this way, users can navigate through the hierarchical structure
only by typing U/D keys at the right timing.

@@

@@

4-way navigation are quite common for exploring hierarchical data structure,
and modern computer users have no problem using it.
Many mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for selecting an item from a list and 
the push button is used for moving to the next level.
PowerMate is equipped with a push button which can used for such purposes.
As far as we know,
Strotor is the only interaction method for exploring hierarchical data structure
with only two keys or one rotating device.

@@

\bibliographystyle{plain}
\bibliography{paper}

>>>>

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate two key signals based on the direction of the rotation.
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique and device called ``Strotor'',
where users can explore large hierarchical database by simple rotating operation.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 306 110]{figures/rotation.pdf}}
\caption{Using a rotation device for generating key events.}
\label{rotation}
\end{figure}

@@

Stroter's behavior is based on the following simple principles.
Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
They can be generated either by rotating the Strotor device or typing a keyboard.

\begin{enumerate}
\item A portion of a hierarchical data is shown to the user.

\item Always one element in the hierarchical data is selected and highlighted.

% \item Display the selected element, its siblings, its ancestors and their siblings.

\item When an elemented is selected, its siblings, its ancestors and their siblings are displayed
around the selected elememt.

\item Users can generate U to select the new element above the currently selected element,
and generate D to select the new element below the selected element.
Whenever the selection is changed, 3. is performed.
If the depth of the newly selected element is different from the currently
selected element, siblings of the currently selected element will disappear.

\item When a newly selected element has children and the user does no further operations,
the first child of the selected elemented is selected, and 3. is performed.
As a result, all the siblings of the newly selected element
(the first child of the currently selected elmeent) appear in the list.

\end{enumerate}

We show how Strotor works, using a hierarchical data structure of
shops list in a shopping mall shown in Figure \ref{fig1}.
Rectangles with thick border represent categories, and
other rectangles represent individual shops.

\begin{figure}[H]
% \includegraphics[width=70mm]{figures/fig1.pdf}
\centerline{\includegraphics[width=80mm,bb=0 0 490 490]{figures/fig1.pdf}}
\caption{Sample data: shops in a shopping mall.}
\label{fig1}
\end{figure}

When the user starts the exploration, only the shops and categories
at the top level are displayed (Figure \ref{fig2}).
When the user generates D,
the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).

@@

If the user generates D two more times, 
\tsf{Food/drink} category is selected (Figure \ref{fig4}).
If the user stops the operation and waits for a moment, the shops under the \tsf{Food/drink}
category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure \ref{fig5}).

@@

When the user generates D twice and stops the operation,
\tsf{Fresh grocery} category is selected (Figure \ref{fig6}), and
after a short moment,
the shops under the category is automatically selected (Figure \ref{fig7}).

@@

When the user generates U here, \tsf{Fresh grocery} is selected,
the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
If the user generates U two more times, the display changes to the state
shown in Figure \ref{fig5},
and one more U will yield Figure \ref{fig4}.

If the user generates D in Figure \ref{fig4}, the next visible entry
(\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.

@@

When the user generates D twice in Figure \ref{fig7},
\tsf{Clothing} is selected, and the display changes to Figure \ref{fig8}.

In this way, users can explore the hierarchical structure
only by generating U/D keys at the right timing.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=50mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
\caption{PowerMate device used for the Strotor prototype.}
\label{powermate}
\end{figure}

@@

4-way navigation are quite common for exploring hierarchical data structure,
and modern computer users have no problem using it.
Many mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for selecting an item from a list and 
the push button is used for moving to the next level.
PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
To the best of the authors' knowledge,
Strotor is the only interaction method for exploring hierarchical data structure
with one rotating device.

@@

\small{
\bibliographystyle{plain}
\bibliography{paper}
}
